---
title: "Model B"
subtitle: "Effect of Intervention on Financial Recovery after the first Income Support"
author: "Andriy Koval"
format:
  html:
    page-layout: full
    toc: true
    toc-location: right
    code-fold: show
    theme: litera
    highlight-style: nord
    embed-resources: true
    standalone: true
    monofont: consolas
    code-line-numbers: true
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

This script estimates NIA coefficients using multiple time points: the one before IS and all time points AFTER the exit from the first IS spell. Uses intervention-specific balancing weights estimated at `is_timeline == -1L` time point.


<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->

```{r}
#| code-summary: Reconciles working directory between execution modes
#| echo: false
#| results: hide
#| message: false 
cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../') # keep this chunk isolated  
```

```{r}
#| label: set_options
#| code-summary: report-wide formatting options
#| echo: false
#| results: hide
#| message: false 
cat("Working directory: ", getwd()) # turn on to test the location
report_render_start_time <- Sys.time()
# set options shared by all chunks
opts_chunk$set(
  results      = 'show',
  message      = FALSE,
  warning      = FALSE,
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400, # dots per inch,
  # out.width  = "650px", # pixels, this affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6, # inches
  fig.height   = 4, # inches
  fig.path     = 'figure-png-iso/' # where figures are stored
  ,cache = TRUE
)
echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) # number of characters to display in the output (dflt = 80)
ggplot2::theme_set(ggplot2::theme_bw()) # common theme for all graphs
read_chunk("./analysis/8-model-B/model-B.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```


# Environment

This section reviews the components of the working environment of the report. Non-technical readers are welcomed to skip. Come back if you need to understand the origins of custom functions, scripts, or data objects.

```{r}
#| label: load-packages
#| code-summary: Packages used in the current report
#| echo: true
#| results: hide
#| message: false
#| code-fold: true
```

```{r}
#| label: load-sources
#| code-summary: Collection of custom functions used in current repository 
#| echo: true
#| results: hide
#| message: false
#| code-fold: true
```

```{r}
#| label: declare-globals
#| code-summary: Values used throughout the report.
#| echo: true
#| results: hide
#| message: false 
#| code-fold: true
```

```{r}
#| label: declare-globals-hidden
#| code-summary: Values used throughout the report the must NOT show up in report.
#| echo: false
#| results: hide
#| message: false 
#| code-fold: false
```

```{r}
#| label: declare-functions
#| code-summary: Custom functions defined for use in this report.
#| echo: true
#| results: hide
#| message: false 
#| code-fold: true
```

# Context

Please see `EDA-tax_year` for detailed description of all relevant tables. Here, we providing a brief summary as a reminder.

-   Derivatives of `ds_tax_year`:

    -   `ds0` - verbatim copy of `ds_tax_year`, one row = one year of tax data

    -   `ds1` - adds filters for suspicious values/outliers of the outcomes

    -   `ds2` - adds new convenience variables, added covariates from `ds_covars`

    -   `ds3` - drops cases with suspicious values (convenient for models and graphs)

    -   `ds3_long` - `ds3` pivoted longer with respect to **timeline variables** (years to IS, tax year, age) and **outcome variables** (total earnings, total income, and their logs)

    -   `ds4` - specific to the chosen outcome (in this case, `earnings_total`). Labels and tidies the levels of factor variables.

    -   `ds5` - prepares data for the model of a particular type (e.g. A, B, etc., however we specify it).

```{r}
#| label: load-data
#| code-summary: Load data rectangles to be used in the report
#| warning: false
#| cache: true
#| results: markup
#| echo: true
#| code-fold: true
```

```{r}
#| label: tweak-data-0
#| code-summary: Creates data state `ds5B`, prepared for the use by Model B (the year before IS and all years after IS).
#| echo: true
#| results: hide
#| message: false
#| cache: true
#| code-fold: true
```

```{r}
#| label: tweak-data-1
#| code-summary: Creates form `ds1`. Adds filters for questionable values of the outcome
#| echo: true
#| results: hide
#| message: false
#| cache: true
#| code-fold: true
```

# Data

To recollect the structure of longitudinal data, examine a single case:

```{r results='show', message=FALSE, echo=T, class.source="fold-hide" }
#| code-summary: View for one person in `ds4`
#| results: hold
#| code-fold: true
ds4 %>% 
  filter(person_oid == sample_of_interest1) %>% 
  select(1:2, earnings_total, timeline_is, waveF, outcome_before) %>% 
  mask_ids()
```

For the purposes of the current model (`model-B`), which evaluates change between multiple time points ( the year before IS and all years after IS), we filter the data set to keep only relevant time points.

```{r results='show', message=FALSE, echo=T, class.source="fold-hide" }
#| code-summary: View for the same person in `ds5B`
#| results: hold
#| code-fold: true
ds5B %>% 
  filter(person_oid == sample_of_interest1) %>% 
  select(1:2, earnings_total, timeline_is, waveF, waveL, outcome_before) %>% 
  mask_ids()
```

```{r}
#| code-summary: a person who did NOT have a given intervention, `career_planning`

ds5B %>%
 keep_random_id(seed=45) %>%
 mask_ids() %>%
 select(all_of(c(design,outcomes,intervention[1], covariates[1:2]))) %>%
 print()
```

```{r}
#| code-summary: a person who did have a given intervention
ds5B %>%
 keep_random_id(seed=4) %>%
 mask_ids() %>%
 select(all_of(c(design,outcomes,intervention[1], covariates[1:2]))) %>%
 print()
```

We measure **INTERVENTION** as the

> number of events before the END of the first IS spell

Note, that currently we do not limit a look-back window, which means we do not know **when exactly** the intervention took place: *before* the person started Income Support or *after* they exited from the program. This is important to remember when interpreting model results.

# Variables

We organize our rectangle into the following groups of variables: design, outcomes, covariates, and interventions. This section reviews their distributional properties

## Design

```{r}
#| label: inspect-design
#| code-summary: Summarize design variables
```

<!-- ## Outcomes -->

<!-- ```{r} -->

<!-- #| label: inspect-outcomes -->

<!-- #| code-summary: Summarize outcome variables -->

<!-- ``` -->

<!-- ## Covariates -->

<!-- ```{r} -->

<!-- #| label: inspect-covariates -->

<!-- #| code-summary: Summarize covariates variables -->

<!-- ``` -->

<!-- ## Interventions -->

<!-- ```{r} -->

<!-- #| label: inspect-intervention -->

<!-- #| code-summary: Summarize intervention variables -->

<!-- ``` -->

<!-- ## Reference group -->

<!-- ```{r} -->

<!-- #| label:  empirical-reference-group -->

<!-- #| code-summary: Derive an empirical reference group -->

<!-- ``` -->

<!-- Note that the size of the empirical reference group is quite small ( n = 4) and maybe misleading about where the "centre of gravity" is in this manifold of descrete covariates.  -->

<!-- # Demographics -->

<!-- ```{r} -->

<!-- #| label: sex-marital-children -->

<!-- #| code-summary: Explore groups prevalent in sex-marital-children variables -->

<!-- #| fig.width: 10 -->

<!-- #| fig.height: 7 -->

<!-- #| out.width: 1000 px -->

<!-- d <- -->

<!--   ds5B %>% -->

<!--   filter(waveL==0) %>%  -->

<!--   group_by(sex2, dependent2, marital2) %>% -->

<!--   summarize( -->

<!--     person_count = n_distinct(person_oid) -->

<!--     ,earnings_median = median(earnings_total, na.rm = T) -->

<!--     ,age_median = median(age_in_seq, na.rm = T) -->

<!--     # ,earnings_mean = mean(earnings_total, na.rm = T) -->

<!--     # ,age_mean = mean(age_in_years, na.rm = T) -->

<!--     ,.groups = "drop" -->

<!--   ) %>% -->

<!--   mutate( -->

<!--     total_count = sum(person_count) -->

<!--     ,person_prop = person_count/total_count -->

<!--     ,person_pct = scales::percent(person_prop, accuracy = .1) -->

<!--   ) %>% -->

<!--   # filter(waveL==1) %>% -->

<!--   # filter(!sex2=="Unknown") %>% -->

<!--   # filter(!marital2=="(Missing)") %>% -->

<!--   select(everything()) -->

<!-- # d %>% print_all() -->

<!-- g <- -->

<!--   d %>% -->

<!--   ggplot(aes(y=person_count,x=sex2, fill=dependent2))+ -->

<!--   geom_col(position = position_dodge())+ -->

<!--   geom_label(aes(label = person_pct))+ -->

<!--   facet_wrap(c("marital2"))+ -->

<!--   scale_y_continuous(breaks = seq(0,10000,1000), labels = scales::comma_format())+ -->

<!--   labs( -->

<!--     title = "Size of the group (sex-marital-dependents) as percent from total" -->

<!--     ,subtitle = "Groups (bars) are mutually exclusive and exhausive:" -->

<!--   ) -->

<!-- g -->

<!-- ``` -->

# Session Information {#session-info}

For the sake of documentation and reproducibility, the current report was rendered in the following environment. Click the line below to expand.

<details>

<summary>Packages used</summary>

Packages used in current report

```{r}
#| label: session-info
#| echo: false
#| code-fold: true
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
}
```

</details>

```{r}
#| label: session-duration
#| echo: false
#| code-fold: true
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
