---
title: "FIESTA Phase 3 Results"
subtitle: "Typical Sequence of CEIS Workshops"
author: 
  - Andriy Koval
format:
  html:
    page-layout: full
    toc: true
    toc-location: right
    code-fold: show
    theme: litera
    highlight-style: nord
    embed-resources: true
    standalone: true
    monofont: consolas
    code-line-numbers: true
    df-print: paged
    out.width: 900px
editor: visual
editor_options: 
  chunk_output_type: console
---

Examines the sequence of workshops undertaken by the research population of the FIESTA Project

# Definitions

> **FIESTA Inclusion Criteria** - Albertans who received Income Support for the first time in 2014 - 2019 fiscal years.

> **Research Question** - What is a typical sequence of engaging CEIS Workshops around the time of engaging Income Support program?

> **Window of Observation** - from 12 months prior to the start of Income Support to the end

# Environment

> Reviews the components of the working environment of the report. Non-technical readers are welcomed to skip. Come back if you need to understand the origins of custom functions, scripts, or data objects.

```{r}
#| echo: false
#| code-fold: true
 rm(list = ls(all.names = TRUE)) 
if(exists("clear_memory")){
  if(clear_memory){
    rm(list = ls(all.names = TRUE)) # Clear the memory of variables from previous run.
  }
}
```

```{r}
#| label: set_options
#| echo: false
#| code-fold: true
#| warning: false
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any 
# NOTE: set wd to source file location while working within QMD
options(width=100) # number of characters to display in the output (dflt = 80)
```




```{r}
#| label: load-packages
#| code-summary: Packages used in the current report
#| echo: true
#| results: hide
#| message: false
#| code-fold: true
#| warning: false
#| code-overflow: wrap
library(dplyr) # data wrangling
library(readr)
library(tidyr)
library(cowplot)
library(ggalluvial)
library(scales)
# -- 2.Import only certain functions of a package into the search path.
import::from("magrittr", "%>%")
# -- 3. Verify these packages are available on the machine, but their functions need to be qualified: http://r-pkgs.had.co.nz/namespace.html#search-path
requireNamespace("DBI"         ) # database
requireNamespace("odbc"        ) # database
requireNamespace("readr"    )# data import/export
```

```{r}
#| label: load-sources
#| code-summary: Collection of custom functions used in current repository 
#| echo: true
#| results: hide
#| message: false
#| warning: false
#| code-fold: true
base::source("./scripts/common-functions.R") # project-level
base::source("./scripts/operational-functions.R") # project-level

```

```{r}
#| label: declare-globals
#| code-summary: Values used throughout the report.
#| echo: true
#| results: hide
#| message: false 
#| code-fold: true
# printed figures will go here:
# prints_folder <- paste0("./analysis/phase-3-results/prints/")
# if(!file.exists(prints_folder)){dir.create(file.path(prints_folder))}

# visual style applied to all graphs
baseSize <- 10
ggplot2::theme_set(
  ggplot2::theme_bw(
  )+
    theme(
      strip.background = element_rect(fill="grey95", color = NA)
      ,panel.grid = element_line(color = "grey95")
      ,panel.border = element_rect(color = "grey80")
      ,axis.ticks = element_blank()
      ,text=element_text(size=baseSize)
    )
) # set common theme for all graphs

# corporate colors
abcol <- c(
  "stone"     = "#5f6a72" # stone   - grey
  ,"dusk"     = "#d40072" # dusk    - magenta
  ,"sunset"   = "#ff7900" # sunset  - brown
  ,"pasture"  = "#77b800" # pasture - green
  ,"sky"      = "#00aad2" # sky     - blue
  ,"prairie"  = "#edb700" # prairie - yellow
)

(prints_folder <- paste0("./analysis/phase-3-results/prints-sankey/")) # local
if (!fs::dir_exists(prints_folder)) { fs::dir_create(prints_folder) }

fold0_colors <- c(
  "Career Planning"               = "#1b9e77"
  ,"Exposure Course"              = "#7570b3"
  ,"Job Placement"                = "#d95f02"
  ,"None"                  = "grey50"
  ,"Workshop"              = "#e5d8bd"
  
  ,"Cover Letters"                = "#8dd3c7"
  ,"Interview Skills"             = "#bebada"
  ,"Job Search"                   = "#fb8072"
  ,"Labour Market Information"    = "#80b1d3"
  ,"Resume Writing"               = "#fdb462"
  ,"Self Assessment"              = "#b3de69"
)

intervention_matrix <- tibble::tribble(
  ~program_class1     , ~fold0                    ,~fold1             , ~fold2,
  "Assessment"        , "Employability"                 ,"EA"               ,"EA",
  "Assessment"        , "Needs Identification"          ,"EA"               ,"EA",
  "Assessment"        , "Service Needs Determination"   ,"EA"               ,"EA",
  "Career Information", "Exposure Course"               ,"Exposure Course"  ,"Exposure Course",
  "Career Information", "Job Placement"                 ,"Job Placement"    ,"Job Placement",
  "Career Information", "Career Planning"               ,"Career Planning"  ,"Workshop",
  "Career Information", "Job Search"                    ,"Workshop"         ,"Workshop",
  "Career Information", "Resume Writing"                ,"Workshop"         ,"Workshop",
  "Career Information", "Cover Letters"                 ,"Workshop"         ,"Workshop",
  "Career Information", "Interview Skills"              ,"Workshop"         ,"Workshop",
  "Career Information", "Labour Market Information"     ,"Workshop"         ,"Workshop",
  "Career Information", "Self Assessment"               ,"Workshop"         ,"Workshop",
  "Career Information", "Workshop(Other)"               ,"Workshop"         ,"Workshop",
  "Training for Work" , "Training for Work"             ,"Training for Work","Training for Work",
  "Work Foundations"  , "Work Foundations"              ,"Work Foundations" ,"Work Foundations",
)
# intervention_matrix %>% neat()
```

```{r}
#| label: declare-functions
#| code-summary: Custom functions defined for use in this report.
#| echo: true
#| results: hide
#| message: false 
#| code-fold: true
```

# Data

```{r }
#| label: load-data
#| code-summary: Bring in results of Phase 3 modeling
#| warning: false
#| cache: true
#| code-fold: true
#| code-overflow: wrap

# Workshop(Other) is broken down into more granular categories 
wk_freq_fold0  <- readr::read_csv("./analysis/phase-3-results/data/2024-03-13/freq-intervention.csv")
wk_order_fold0 <- readr::read_csv("./analysis/phase-3-results/data/2024-03-13/alluvial-intervention.csv") %>% 
  mutate_at( # to align with fold1
    .vars = c("wk1","wk2","wk3")
    ,.funs = ~stringr::str_remove(.,"\\(Other\\)")
  )

# Highest granularity of Intervention
wk_freq_fold1  <- readr::read_csv("./analysis/phase-3-results/data/2024-03-13/freq-fold1.csv")
wk_order_fold1 <- readr::read_csv("./analysis/phase-3-results/data/2024-03-13/alluvial-fold1.csv")

# Sample size of Intervention occurrence and observed outcomes within profiles
ds_unbalanced <- readr::read_csv("./analysis/phase-3-results/data/2024-03-14/unbalanced-outcome-table.csv")

```

```{r}
#| label: compute-values
#| code-summary: Computes fundamental values for the use in annotations
#| cache: true
#| code-fold: true

fiesta_n <- 
  ds_unbalanced %>% 
  filter(waveL==0L) %>% 
  summarize(fiesta_total = sum(sample_size)) %>% 
  pull(fiesta_total) %>% as.integer()

fiesta_n_no_ceis <- 
  ds_unbalanced %>% 
  filter(waveL==0L) %>% 
  filter(wk_combo == "__ + __ + __ + __") %>% 
  summarize(fiesta_no_ceis = sum(sample_size)) %>% 
  pull(fiesta_no_ceis) %>% as.integer()

fiesta_n_with_ceis <- 
  ds_unbalanced %>% 
  filter(waveL==0L) %>% 
  filter(wk_combo != "__ + __ + __ + __") %>% 
  summarize(fiesta_with_ceis = sum(sample_size)) %>% 
 pull(fiesta_with_ceis) %>% as.integer()

```

`r scales::comma(fiesta_n)` - Number of clients who had their first Income Support in 2014-19 FY **and** whose *Total Earnings* were recovered from T1 tax files for at least two time points (in the years immediately before and after their IS spell)

`r scales::comma(fiesta_n_no_ceis)` - Number of clients who did not take any CEIS workshops about the time of their first Income Support (from 12 months prior to the start to the end of the IS spell). However, they may have taken non-CEIS intervention (e.g. Work Foundations, Training for Work) or some employability assessment.

`r scales::comma(fiesta_n_with_ceis)` - Number of clients with at least one CEIS workshop about the time of their first Income Support spell.

# Context

```{r}
#| label: context-1
#| code-summary: FIESTA sample size
#| cache: false
#| code-fold: true
#| fig-width: 9
#| fig-height: 2.5


d <- 
  ds_unbalanced %>% 
  filter(waveL==0L) %>% 
  # select(2:4) %>% 
  mutate(
    wk_profile = case_when(
      wk_combo == "__ + __ + __ + __" ~ "No CEIS workshop",
      TRUE ~ "At least one CEIS workshop"
    )
  ) %>% 
  group_by(wk_profile) %>% 
  summarize(
    n = sum(sample_size)
    ,.groups = "drop"
  ) %>% 
  mutate(
    prop = n/sum(n)
    ,pct = percent(prop)
  )


g <- 
  d %>% 
  ggplot(aes(x=1, y =n ,  label = pct, fill = wk_profile))+
  geom_col(position = "stack")+
  geom_text(position = position_stack(vjust = .5))+
  scale_x_continuous(breaks = NULL)+
  scale_y_continuous(labels = comma_format())+
  coord_flip()+
  scale_fill_manual(values = c( as.vector(c(abcol["sunset"],abcol["sky"]))))+
  labs(
    x = NULL
    ,y = NULL
    ,title = "FIESTA research population (first Income Support in 2014-2019 FY + known eranings before and after IS)"
    ,subtitle = paste0("Total: ",scales::comma(fiesta_n), " | Without any CEIS workshop between 12 months prior and the end of IS: ",comma(fiesta_n_no_ceis), " |  With at least one CEIS WK: ", comma(fiesta_n_with_ceis) )
    ,fill = NULL
  )+
  theme(
    legend.position = "bottom"
  )+
  guides(
    fill = guide_legend(reverse=TRUE)
  )
g %>% quick_save("contex-1",w=9,h=2.5)
g
```

Current analysis phase (FIESTA-3) focuses on estimating the impact of specific CEIS workshops, some of which engage fewer clients than others. To maintain sufficient sample size for estimating the net impact, we resorted to distinguishing only 4 categories of workshops: Career Planing, Exposure Course, Job Placement and Workshop (Other). We refer to this granularity as `fold0`. The last category, *Workshop (Other)* (or just *Workshop* for brevity) includes all other CEIS workshops (e.g. Resume Writing, Cover Letters, Interview Skills, etc). We preserve this granularity as `fold1` and use it in selective exploratory graphs of this report.

```{r}
#| label: context-2
#| code-summary: Granularity of the Intervention
#| cache: false
#| code-fold: true
#| fig-width: 9
#| fig-height: 2.5
#| df-print: responsive

intervention_matrix %>% filter(program_class1=="Career Information") %>% select(fold0,fold1) %>% gt::gt()

```


# Fold 1 - Table

```{r}
#| code-summary: Prepare data table
#| code-fold: true
#| cache: true 

d1 <-
  wk_order_fold1 %>% 
  mutate( # explicit NA and factors
     wk1 = forcats::fct_na_value_to_level(wk1,"None")
     ,wk2 = forcats::fct_na_value_to_level(wk2,"None")
     ,wk3 = forcats::fct_na_value_to_level(wk3,"None")
  )
```

::: panel-tabset
## First

```{r}
#| code-fold: true
#| cache: true

d1 %>% 
  group_by(wk1) %>% 
  summarize(count = sum(person_count)) %>% 
  ungroup() %>% 
  mutate(
        total = sum(count)
    ,prop = count/sum(count)
    ,pct = percent(prop, accuracy = 1)
    ,label = paste0(wk1," (", comma(count),",",pct,")")
  ) %>% 
  neat()
```

## Second

```{r}
#| code-fold: true
#| cache: true

d1 %>% 
  group_by(wk2) %>% 
  summarize(count = sum(person_count) ) %>% 
  ungroup() %>% 
  mutate(
    total = sum(count)
    ,prop = count/sum(count)
    ,pct = percent(prop, accuracy = 1)
    ,label = paste0(wk2," (", comma(count),",",pct,")")
  ) %>% 
  mutate(
    total_wk2 = total - count[which(wk2=="None")]
    ,total_wk2 = case_when(!wk2=="None"~total_wk2)
    ,prop_wk2 = count/total_wk2
    ,pct_wk2 = percent(prop_wk2, accuracy =1)
    ,label_wk2 = paste0(wk2," (", comma(count),",",pct_wk2,")")
  ) %>% 
  select(-c("prop","prop_wk2")) %>% 
   neat() 
```

## Third

```{r}
#| code-fold: true
#| cache: true

d1 %>% 
  group_by(wk3) %>% 
  summarize(count = sum(person_count) ) %>% 
  ungroup() %>% 
  mutate(
    total = sum(count)
    ,prop = count/sum(count)
    ,pct = percent(prop, accuracy = 1)
    ,label = paste0(wk3," (", comma(count),",",pct,")")
  ) %>% 
  mutate(
    total_wk3 = total - count[which(wk3=="None")]
    ,total_wk3 = case_when(!wk3=="None"~total_wk3)
    ,prop_wk3 = count/total_wk3
    ,pct_wk3 = percent(prop_wk3, accuracy =1)
    ,label_wk3 = paste0(wk3," (", comma(count),",",pct_wk3,")")
  ) %>% 
  select(-c("prop","prop_wk3")) %>% 
   neat() 

```
:::

# Fold 1 - Graph

::: panel-tabset
## First

```{r}
#| label: fold1-table
#| code-fold: true
#| warning: false
#| fig-width: 12
#| fig-height: 7
#| out.width: "1200px"
#| cache: false

g1 <- 
  d1 %>% 
  arrange(wk2) %>% 
  ungroup() %>% 
  ggplot(
    aes(
      axis1  = wk1
      ,axis2 = wk2
      ,axis3 = wk3
      ,y     = person_count    
      ,fill = wk1
      
      )
      
  ) +
  geom_alluvium( stat = "flow") +
  geom_stratum(stat ="stratum")+
  # geom_stratum(aes(fill=wk1),alpha = .5, width = 1/3) +
  # geom_flow(aes(fill = wk2),aes.flow = "forward")+
  # scale_fill_manual(values = combo_colors)+
  geom_text(stat = "stratum",aes(label = after_stat(stratum)), size = baseSize-7) +
  # geom_text(stat = "stratum",label = c("1","2","3","4","5","6","7", "8","9"))+#,"10"#,"11", "12","13","14")) +
  # geom_text(stat = "stratum",label = c("1","2","3","4","5","6","7", "8","9","10"))+##,"11", "12","13","14")) +
  scale_x_discrete(limits = c("First", "Second", "Third"),
                   expand = c(0.15, 0.05)) +
  scale_y_continuous(labels = comma_format())+
  # theme_void()+
  scale_fill_manual(values = fold0_colors)+
  guides(fill=guide_legend(ncol =1))+
  labs(
    fill = "Workshop"
    ,title = "Sequence of CEIS workshop in FIESTA sample"
    ,subtitle = paste0("Total: ",scales::comma(fiesta_n), " | With at least one CEIS workshop: ",comma(fiesta_n_with_ceis), " | Without any CEIS: ", comma(fiesta_n_no_ceis) )
    ,y = "Number of clients"
    ,x = "The order of the CEIS workshop ( 12 months prior to start - end of IS) "
  )+
  theme(
    text = element_text(size = baseSize+5)
  )
g1
```

## Second

```{r }
#| code-fold: true
#| warning: false
#| cache: false
#| fig-width: 12
#| fig-height: 7

g1 %+% aes(fill=wk2) %+%labs(fill="Workshop")
```

## Third

```{r fig.width=9, fig.height=5}
#| code-fold: true
#| warning: false
#| cache: false
#| fig-width: 12
#| fig-height: 7

g1 %+% aes(fill=wk3)%+%labs(fill="Workshop")
```
:::


# Fold 0

::: panel-tabset
## First

```{r}
#| code-fold: true
#| warning: false
#| cache: true
d0 <-
  wk_order_fold0 %>% 
  filter(!wk1 %in% c("Career Planning","Exposure Course","Job Placement")) %>% 
  filter(!is.na(wk2), !is.na(wk3))

g0 <- 
  d0 %>% 
  ungroup() %>% 
  ggplot(
    aes(
      axis1  = wk1
      ,axis2 = wk2
      ,axis3 = wk3
      ,y     = person_count    
      ,fill = wk1
      )
  ) +
  geom_alluvium(stat = "flow") +
  geom_stratum() +
  geom_text(stat = "stratum",
            aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("First", "Second","Third"),
                   expand = c(0.15, 0.05)) +
  scale_fill_manual(values = fold0_colors)+
  # theme_void()+
  guides(fill=guide_legend(ncol =1))+
  labs(
    fill = "Workshop"
    ,title = "Sequence of CEIS workshop in FIESTA sample"
    ,subtitle = paste0("Total: ",scales::comma(fiesta_n), " | With at least one CEIS workshop: ",comma(fiesta_n_with_ceis), " | Without any CEIS: ", comma(fiesta_n_no_ceis) )
  )
g0
```

## Second

```{r}
#| code-fold: true
#| warning: false
#| cache: true

g0 %+% aes(fill= wk2)
```

## Third

```{r}
#| code-fold: true
#| warning: false
#| cache: true

g0 %+% aes(fill= wk3)
```
:::

```{r}
# see https://ggplot2.tidyverse.org/reference/gg-add.html
g0 %>% quick_save("fiesta_3_sankey-0-3", w=16, h = 9)
```
