---
title: "FIESTA Phase 3 Results"
subtitle: "Typical Sequence of Workshops"
author: 
  - Andriy Koval
format:
  html:
    page-layout: full
    toc: true
    toc-location: right
    code-fold: show
    theme: litera
    highlight-style: nord
    embed-resources: true
    standalone: true
    monofont: consolas
    code-line-numbers: true
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---


Examines the sequence of workshops undertaken by the research population of the FIESTA Project, those who received Income Support for the first time in 2014 - 2019 fiscal years.

# Definitions

> Research Question - What is a typical sequence of engaging CEIS Workshops around the time of engaging Income Support program?
>
> Window of Observation - from 12 months prior to the start of Income Support to the end

# Environment

> Reviews the components of the working environment of the report. Non-technical readers are welcomed to skip. Come back if you need to understand the origins of custom functions, scripts, or data objects.

```{r}
#| echo: false
#| code-fold: true
 rm(list = ls(all.names = TRUE)) 
if(exists("clear_memory")){
  if(clear_memory){
    rm(list = ls(all.names = TRUE)) # Clear the memory of variables from previous run.
  }
}
```

```{r}
#| echo: false
#| code-fold: true
#| warning: false
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any 
```

```{r}
#| label: load-packages
#| code-summary: Packages used in the current report
#| echo: true
#| results: hide
#| message: false
#| code-fold: true
#| warning: false
#| code-overflow: wrap
library(dplyr) # data wrangling
library(readr)
library(tidyr)
library(cowplot)
library(ggalluvial)
library(scales)
# -- 2.Import only certain functions of a package into the search path.
import::from("magrittr", "%>%")
# -- 3. Verify these packages are available on the machine, but their functions need to be qualified: http://r-pkgs.had.co.nz/namespace.html#search-path
requireNamespace("DBI"         ) # database
requireNamespace("odbc"        ) # database
requireNamespace("readr"    )# data import/export
```

```{r}
#| label: load-sources
#| code-summary: Collection of custom functions used in current repository 
#| echo: true
#| results: hide
#| message: false
#| warning: false
#| code-fold: true
base::source("./scripts/common-functions.R") # project-level
base::source("./scripts/operational-functions.R") # project-level

```

```{r}
#| label: declare-globals
#| code-summary: Values used throughout the report.
#| echo: true
#| results: hide
#| message: false 
#| code-fold: true
# printed figures will go here:
# prints_folder <- paste0("./analysis/phase-3-results/prints/")
# if(!file.exists(prints_folder)){dir.create(file.path(prints_folder))}

#| label: declare-globals
#| code-summary: Values used throughout the report.
#| echo: true
#| results: hide
#| message: false 
#| code-fold: true

# visual style applied to all graphs
baseSize <- 10
ggplot2::theme_set(
  ggplot2::theme_bw(
  )+
    theme(
      strip.background = element_rect(fill="grey95", color = NA)
      ,panel.grid = element_line(color = "grey95")
      ,panel.border = element_rect(color = "grey80")
      ,axis.ticks = element_blank()
      ,text=element_text(size=baseSize)
    )
)

# corporate colors
abcol <- c(
  "stone"     = "#5f6a72" # stone   - grey
  ,"dusk"     = "#d40072" # dusk    - magenta
  ,"sunset"   = "#ff7900" # sunset  - brown
  ,"pasture"  = "#77b800" # pasture - green
  ,"sky"      = "#00aad2" # sky     - blue
  ,"prairie"  = "#edb700" # prairie - yellow
)

(prints_folder <- paste0("./prints-sankey/")) # local
if (!fs::dir_exists(prints_folder)) { fs::dir_create(prints_folder) }

```

```{r}
#| label: declare-functions
#| code-summary: Custom functions defined for use in this report.
#| echo: true
#| results: hide
#| message: false 
#| code-fold: true
```

# Data

Bring in the results of the Phase 3 modeling

```{r }
#| label: load-data
#| code-summary: Define SQL query to send to the database
#| warning: false
#| cache: true
#| code-fold: true
#| code-overflow: wrap


# wk_freq_fold1  <- readr::read_csv("./analysis/phase-3-results/data/2024-03-13/freq-fold1.csv")
wk_order_fold1 <- readr::read_csv("./analysis/phase-3-results/data/2024-03-13/alluvial-fold1.csv")

# wk_freq_fold0  <- readr::read_csv("./analysis/phase-3-results/data/2024-03-13/freq-intervention.csv")
wk_order_fold0 <- readr::read_csv("./analysis/phase-3-results/data/2024-03-13/alluvial-intervention.csv")

ds_unbalanced <- readr::read_csv("./analysis/phase-3-results/data/2024-03-14/unbalanced-outcome-table.csv")

```

```{r}
#| label: compute-values
#| code-summary: Computes fundamental values for the use in annotations
#| cache: true
#| code-fold: true

fiesta_n <- 
  ds_unbalanced %>% 
  filter(waveL==0L) %>% 
  summarize(fiesta_total = sum(sample_size)) %>% 
  pull(fiesta_total) %>% as.integer()

fiesta_n_no_ceis <- 
  ds_unbalanced %>% 
  filter(waveL==0L) %>% 
  filter(wk_combo == "__ + __ + __ + __") %>% 
  summarize(fiesta_no_ceis = sum(sample_size)) %>% 
  pull(fiesta_no_ceis) %>% as.integer()

fiesta_n_with_ceis <- 
  ds_unbalanced %>% 
  filter(waveL==0L) %>% 
  filter(wk_combo != "__ + __ + __ + __") %>% 
  summarize(fiesta_with_ceis = sum(sample_size)) %>% 
 pull(fiesta_with_ceis) %>% as.integer()

```

# Workshop Sequence

```{r}
d1 <-
  wk_order_fold1 %>% 
  mutate( # explicit NA and factors
     wk1 = forcats::fct_na_value_to_level(wk1,"None")
     ,wk2 = forcats::fct_na_value_to_level(wk2,"None")
     ,wk3 = forcats::fct_na_value_to_level(wk3,"None")
  )
# stratum_labels <- 
#   
  d1 %>% 
  group_by(wk1) %>% 
  summarize(count = sum(person_count)) %>% 
  ungroup() %>% 
  mutate(
        total = sum(count)
    ,prop = count/sum(count)
    ,pct = percent(prop, accuracy = 1)
    ,label = paste0(wk1," (", comma(count),",",pct,")")
  ) %>% 
  print()

  d1 %>% 
  group_by(wk2) %>% 
  summarize(count = sum(person_count) ) %>% 
  ungroup() %>% 
  mutate(
    total = sum(count)
    ,prop = count/sum(count)
    ,pct = percent(prop, accuracy = 1)
    ,label = paste0(wk2," (", comma(count),",",pct,")")
  ) %>% 
  print()

combo_colors <- c(
  "Career Planning" = "red"
  ,"Exposure Course" = "blue"
  ,"Job Placement" = "green"
  ,"None" = "grey"
)
g1 <- 
  d1 %>% 
  arrange(wk2) %>% 
  ungroup() %>% 
  ggplot(
    aes(
      axis1  = wk1
      ,axis2 = wk2
      ,axis3 = wk3
      ,y     = person_count    
      # ,fill = wk2
      # , color = wk1
      )
      
  ) +
  geom_alluvium(aes(fill = wk2), stat = "flow") +
  geom_stratum()+
  # geom_stratum(aes(fill=wk1),alpha = .5, width = 1/3) +
  # geom_flow(aes(fill = wk2),aes.flow = "forward")+
  # scale_fill_manual(values = combo_colors)+
  geom_text(stat = "stratum",aes(label = after_stat(stratum))) +
  # geom_text(stat = "stratum",label = c("1","2","3","4","5","6","7", "8","9"))+#,"10"#,"11", "12","13","14")) +
  # geom_text(stat = "stratum",label = c("1","2","3","4","5","6","7", "8","9","10"))+##,"11", "12","13","14")) +
  scale_x_discrete(limits = c("First", "Second"),
                   expand = c(0.15, 0.05)) +
  scale_y_continuous(labels = comma_format())+
  # theme_void()+
  guides(fill=guide_legend(ncol =1))+
  labs(
    fill = "Workshop"
    ,title = "Sequence of CEIS workshop in FIESTA sample"
    ,subtitle = paste0("Total: ",scales::comma(fiesta_n), " | With at least one CEIS workshop: ",comma(fiesta_n_with_ceis), " | Without any CEIS: ", comma(fiesta_n_no_ceis) )
    ,y = "Number of clients"
  )
g1
g1 %>% quick_save("fiesta_3_sankey-1", w=16, h = 9)
```

```{r}
d0 <-
  wk_order_fold0 %>% 
  filter(!wk1 %in% c("Career Planning","Exposure Course","Job Placement")) 

g0 <- 
  d0 %>% 
  ungroup() %>% 
  ggplot(
    aes(
      axis1  = wk1
      ,axis2 = wk2
      ,axis3 = wk3
      ,y     = person_count    )
  ) +
  geom_alluvium(aes(fill = wk1)) +
  # geom_stratum(aes(fill = wk1)) +
  geom_text(stat = "stratum",
            aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("First", "Second","Third"),
                   expand = c(0.15, 0.05)) +
  # theme_void()+
  guides(fill=guide_legend(ncol =1))+
  labs(
    fill = "Workshop"
    ,title = "Sequence of CEIS workshop in FIESTA sample"
    ,subtitle = paste0("Total: ",scales::comma(fiesta_n), " | With at least one CEIS workshop: ",comma(fiesta_n_with_ceis), " | Without any CEIS: ", comma(fiesta_n_no_ceis) )
  )
g0
g0 %>% quick_save("fiesta_3_sankey-0", w=16, h = 9)
```
